%-------------------------
% Resume in Latex
% Author : Cameron Long
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Cameron Long}} & Email : \href{mailto:kyameronlong@gmail.com}{kyameronlong@gmail.com}\\
  \href{www.github.com/cdalong}{www.github.com/cdalong} & Mobile : +16463288550 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Victoria}{Victoria, British Columbia}
      {Bachelor of Software Engineering Specializing in Artificial Intelligence
      GPA: 3.83}{Sept 2013 - May 2018}
 
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Associate Software Engineer}{New York, New York}
      {Goldman Sachs}{December 2021 - Present}
      \resumeItemListStart
        \resumeItem{Delphi - Inventory Management}
        {Develop a backed Java platform to manage assets as a replacement for the previously listed system PRIM. Different optimization processes and integration with other systems allows us to reduce the cost of unencumbered assets further than previous techniques. Currently responsible for the deprecation and migration of core feature sets of PRIM to Delphi and integrating Delphi to consume optimisation parameters from other strategic Firm systems }
        \resumeItemListEnd

    \resumeSubheading
      {Associate Software Engineer}{Tokyo, Japan }
      {Goldman Sachs}{December 2020 - December 2021}
      \resumeItemListStart
        \resumeItem{Team Lead - DataLake}
        {Lead a team of three people globally on strategic data platform known as DataLake. Plan and design new software solutions for processing file streams from agent banks and from other internal teams. Delivered 10 Million dollars of PnL impact by the end of Q4 2020}
        \resumeItem{Global Core Liquidity Assets - GCLA}
        {Creating Java and Scala Calculators to aggregate and refine real-time intra-day Cash and High quality assets for Goldman Sachs Japan. HDFS and Spark Calculations are used to provide funding operations with accurate numbers to fund trades using excess cash. Daily GCLA numbers reach over 150 Billion dollars and require extreme accuracy}
        \resumeItemListEnd
    \resumeSubheading
      {Analyst Software Engineer}{Tokyo, Japan}
      {Goldman Sachs}{June 2018 - April 2020}
        \resumeItemListStart
        \resumeItem{Securities and Transaction Reporting Regulation}
        {Rebuilt the matching and trade processing system for TriParty Repo trades using a high performance Java Data Refiner. APAC, US and EMEA regions to transform and link internal trades to external allocations of equity to ensure trading operations are within certain regulatory and Firm risk appetites.}
          \resumeItem{PRIM - Pledge and Realignment Instruction Manager}
          {Managing the daily Liquidity Operations of the Firm by creating a global web-service to process trades and calculate positions. Positions are then moved around the Firm accounts using linear optimization techniques to provide maximal funding benefit and reduced unencumbered assets. 500 Billion USD of equity in 300 thousand products is processed daily by this system.}
        \resumeItem{Delphi Self-Service User Configuration}
        {Exposing configuration of PRIM/Delphi to users to decrease the TTL of configuration changes and easing developer workloads. Created a change management and validation framework to ensure that configurations submitted and approved by users had appropriate oversight and awareness. On-boarding new markets via self-service configuration reduced from two weeks to one day with reduced production risk.}
        \resumeItem{Credit and Liquidity Risk}
        {
        Using Data refinement techniques to expose underlying assets and margin Risk on African government bond repo trades and secured Intercompany loans. Two Billion USD of unencumbered cash can be utilized using this new bond flow for a net Firm profit of 30 Million USD Anually.
        }

      \resumeItemListEnd

    \resumeSubheading
      {Blockchain Consultant}{Calgary, Alberta}
      {Geometric Labs}{May 2017 - January 2018}
      \resumeItemListStart
        \resumeItem{Initial Coin Offerings}
          {Developed Smart Contracts for 3rd Party Ethereum ICOs that raised over 60 Million US Dollars.}
        \resumeItem{Consultation}
          {Worked closely with clients to understand gaps in ticketing and energy markets could benefit from Blockchain technology and propose technical solutions with the release of white papers}
       
      \resumeItemListEnd
      
    \resumeSubheading
    {DevOps Engineer}{Tokyo, Japan}
    {Rakuten}{May 2016 - May 2017}
    \resumeItemListStart
      \resumeItem{Deployment Pipelines}
        {Creating Docker and Kubernetes CI/CD pipelines for auto-deployment of code changes}
     
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Personal}
  \resumeSubHeadingListStart
      \resumeSubItem{Canadian Chamber of Commerce in Japan}
      {Chair of the IT Committee: Managing IT Operations for the CCCJ in regards to client on-boarding and payment management  }
      \resumeSubItem{Game Mods}
      {Created a small, configurable mod for a Unity Game Phasmophobia that allowed players to change in-game parameters based on a config file. The mod had over 30,000 downloads https://github.com/fiskybusiness/phasmophobia}
   
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
   \item{
     \textbf{Technologies}{: Docker, Jenkins, Apache Spark, RabbitMQ, Kubernetes, Springboot, MemSQL, ReactJS, Hadoop}
    }
    \item{
    \textbf{Languages}{: C, Python, C#, C++, SQL, Java, Golang}
     }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
